---
title: "Group Project"
author: "Group 3"
date: "4/8/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

### Data Entry
```{r}
resp <- c(10.87,7.81,11.25,10.33,
          10.35,8.75,11.84,10.69,
          10.3,8.31,11.82,10.31,
          11.03,8.43,12.67,11.56,
          11.3,9.26,12.52,10.95,
          11.34,9.19,12.43,11.4)
mentos <- rep(c(2,4),each=12)
soda <- rep(c("Diet Coke","Coke"),12)
temp <- rep(c("R","R","NR","NR"),6)
```

### Data Frame
```{r include=FALSE}
threeway=data.frame(resp=resp,A=factor(mentos),B=factor(soda),C=factor(temp))
attach(threeway)
```

### Data Matrix
```{r}
datamat=matrix(resp,6,4,byrow=T)
colnames(datamat)=c("B=Diet Coke, C=R","B=Coca-Cola, C=R",
                    "B=Diet Coke, C=NR","B=Coca-Cola, C=NR")
rownames(datamat)=c("A=2","","","A=4","","")
datamat
```

### ANOVA Table
```{r}
outthree=aov(resp~A*B*C,threeway)
summary(outthree)
```

\
Using $\alpha=0.05$, we see that we have factors A, B and C are significant (if we only consider their p-values). We also see an interaction effect between factors B and C being significant. The other interactions aren't significant. 

### Check Residuals
```{r}
fits=outthree$fitted		#same as fitted(junk_out)
res=outthree$residuals	#same as residuals(junk_out)

#Assumption Checking with Residual Plots
par(mfrow=c(2,3))	#create 2 rows and two columns in graphics column
qqnorm(res)
qqline(res)
plot(fits,res,xlab="Y-hat",ylab="Residuals",
     main="Residuals vs. Fits")
plot(res~mentos,vertical=T,xlab="A = Mentos",ylab="Residuals")
stripchart(res~soda,vertical=T,xlab="Treatment",ylab="Anxiety",
           main="Resids vs. Treatment")
stripchart(res~temp,vertical=T,xlab="Treatment",ylab="Anxiety",
           main="Resids vs. Treatment")
par(mfrow=c(1,1))
```

\
A is significant
```{r}
TukeyHSD(outthree, "A")
```

### Mean Matrix
```{r}
# Store means for explaining the interaction plots
meanvec=numeric(8)
count=1
for(i in c(2,4)) {
        for(k in c("R","NR")) {
           for(j in c("Diet Coke","Coke")) {
           meanvec[count]=  mean(resp[mentos==i & soda==j & temp==k]) 
           count = count +1
           }     
        }
}
meanmat=matrix(meanvec,2,4,byrow=T)
colnames(meanmat)=c("B=Diet Coke, C=R","B=Coca-Cola, C=R",
                    "B=Diet Coke, C=NR","B=Coca-Cola, C=NR")
rownames(meanmat)=c("A=2","A=4")
meanmat
```

### Interaction Plots
```{r}
#two factor interactions
par(mfrow=c(1,3))
interaction.plot(A,B,resp,type="b",main="AB")
interaction.plot(A,C,resp,type="b",main="AC")
interaction.plot(B,C,resp,type="b",main="BC")
par(mfrow=c(1,1))
```

Since B:C interaction is significant, we perform analysis on both. 
```{r}
b=2
c=2
n=3
alpha=.05
dfe=16
mse=0.104
Tq=qtukey(1-alpha/(b+c),b,dfe)/sqrt(2)
tuk=numeric(2)
tuknames=numeric(2)
```

### Contrast Comparison for B:C
```{r}
# The effect of B when C=R minus the effect of B when C=NR
bc_ctrst = mean(resp[B=="Diet Coke"&C=="R"]) - mean(resp[B=="Coke"&C=="R"]) -  ( mean(resp[B=="Diet Coke"&C=="NR"]) - mean(resp[B=="Coke"&C=="NR"]) )
se=sqrt(mse*4/6)
mult=qt(1-alpha/3,dfe)
me=mult*se
c(bc_ctrst-me,bc_ctrst,bc_ctrst+me)
```
\
We are 95% confident (at a family level) that the mean liquid loss of Soda-type (B) when it is refrigerated is between 0.41 and 1.64 ounces more than when it is not refrigerated. Therefore, we can say it better at displacing liquid.                     



### Which Combo is best?
```{r}
model.tables(outthree,type="means")
#shows that A=4, B=Diet Coke, C=NR is best closely followed by A=2, B=Diet Coke, C=NR
```

```{r}
#Scheffe
a=2; b=2; c=2; n=3
sch=sqrt((a*b*c-1)*qf(1-alpha,a*b*c-1,dfe)) 
a4b2c1=mean(with(threeway,resp[A==4&B=="Diet Coke"&C=="NR"]))
a2b2c1=mean(with(threeway,resp[A==2&B=="Diet Coke"&C=="NR"]))
pe=a4b2c1-a2b2c1
se=sqrt(2*mse/n)
c(pe-sch*se, pe, pe+sch*se)
```
\
It isn't significantly more. 
